Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-07 paper/paper_new.tex
Changed example images
Fixed figure numbering. (Fig. 7)
Tweaked language in Sect. V.F .

\begin{table}[H]
    \centering
%    \caption{\verb|foreground.mean| statistics for the three Brightness classes}
    \caption{foreground.mean statistics for the three Brightness classes}
    \label{tab:bright}
    \begin{tabular}{cccc}
        \toprule
        \textbf{Class} & \textbf{Mean Intensity} & \textbf{Standard Deviation} & \textbf{Instances}\\
        \midrule
        Dark & 75.2 & 13.5 & 1800\\
        Normal & 93.6 & 14.8 & 5186\\
        Bright & 108.4 & 15.2 & 242\\
        \bottomrule
    \end{tabular}
\end{table}
\subsection{Brightness}
Specimen brightness is one of the 22 hand-recorded metadata properties. It is encoded as \verb|dark|, \verb|normal| or \verb|bright|. These values
correspond to the mean foreground intensity computed by the automated system.
The mean and standard deviation of the foreground intensities were
computed for the images in the three manually specified classes.
Table~\ref{tab:bright} contains the resulting values and shows that
automated intensities values provide objective measures that may be used to break images into groups that correlate with manually generated
brightness classifications.
The mean of \verb|foreground.mean| over all 7,244 images is 89.5, with a
standard deviation of 16.6.
Given that human perception of brightness is quite subjective and
highly variable, we found it problematic to use specific threshold
values to define \verb|dark|, \verb|normal| or \verb|bright| specimens
in concordance with the manually generated metadata.  The technicians
showed little consistency when classifying \verb|normal| or \verb|bright|
specimens. We did find that an 81.2\% accuracy rate could be achieved by
classifying \verb|dark|, as those with a \verb|foreground.mean| of 75
or lower; thus demonstrating that this computed metadata property does 
offer some value when assessing image quality.
% These numbers suggest, for example, that
% \verb|foreground.mean| $\pm$ one-half a standard deviation could define 
% \verb|normal| brightness, with values outside this range being classified
% as \verb|dark| or \verb|bright|.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.49\linewidth]{images/011196_pred}
  \includegraphics[width=0.49\linewidth]{images/011196_mask}
  \includegraphics[width=0.49\linewidth]{images/52399_pred}
  \includegraphics[width=0.49\linewidth]{images/52399_mask}
  \includegraphics[width=0.49\linewidth]{images/56885_pred}
  \includegraphics[width=0.49\linewidth]{images/56885_mask}
  \caption{Examples of masks and bounding boxes from detectron (left) and pixel analysis (right).}
  \label{fig:bbox_mask}
\end{figure}

>>>>

\begin{table}[H]
    \centering
%    \caption{\verb|foreground.mean| statistics for the three Brightness classes}
    \caption{foreground.mean statistics for the three Brightness classes}
    \label{tab:bright}
    \begin{tabular}{cccc}
        \toprule
        \textbf{Class} & \textbf{Mean Intensity} & \textbf{Standard Deviation} & \textbf{Instances}\\
        \midrule
        Dark & 75.2 & 13.5 & 1800\\
        Normal & 93.6 & 14.8 & 5186\\
        Bright & 108.4 & 15.2 & 242\\
        \bottomrule
    \end{tabular}
\end{table}
\subsection{Brightness}
Specimen brightness is one of the 22 hand-recorded metadata properties. It is encoded as \verb|dark|, \verb|normal| or \verb|bright|. These values
correspond to the mean foreground intensity computed by the automated system.
The mean and standard deviation of the foreground intensities were
computed for the images in the three manually specified classes.
Table~\ref{tab:bright} contains the resulting values and shows that
automated intensities values provide objective measures that may be used to break images into groups that correlate with manually generated
brightness classifications.
The mean of \verb|foreground.mean| over all 7,244 images is 89.5, with a
standard deviation of 16.6.
Given that human perception of brightness is quite subjective and
highly variable, we found it problematic to use specific threshold
values to define \verb|dark|, \verb|normal| or \verb|bright| specimens
in concordance with the manually generated metadata.  The technicians
showed little consistency when classifying \verb|normal| versus \verb|bright|
specimens. We did find that an 81.2\% accuracy rate could be achieved by
classifying \verb|dark| images as those with a \verb|foreground.mean| of 75
or less; thus demonstrating that this computed metadata property does 
offer some value when assessing image quality.
% These numbers suggest, for example, that
% \verb|foreground.mean| $\pm$ one-half a standard deviation could define 
% \verb|normal| brightness, with values outside this range being classified
% as \verb|dark| or \verb|bright|.

@@

\begin{figure}[t]
  \centering
  %\includegraphics[width=0.49\linewidth]{images/011196_pred}
  %\includegraphics[width=0.49\linewidth]{images/011196_mask}
  \includegraphics[width=0.49\linewidth]{images/6703_pred}
  \includegraphics[width=0.49\linewidth]{images/6703_mask}
  \includegraphics[width=0.49\linewidth]{images/52399_pred}
  \includegraphics[width=0.49\linewidth]{images/52399_mask}
  %\includegraphics[width=0.49\linewidth]{images/56885_pred}
  %\includegraphics[width=0.49\linewidth]{images/56885_mask}
  \caption{Examples of masks and bounding boxes from detectron (left) and pixel analysis (right).}
  \label{fig:bbox_mask}
\end{figure}
